Storing messages with multipartite neural cliques

### 2014-07-11 Articles/article.tex
...

		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

@@

		Intuitively the choice $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	The probability for all good neurons of a correct cluster (resp. of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_c (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp. $P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)

%	\begin{align*}
%	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
%	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
%	\end{align*}
		\begin{align*}
	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_g(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{l-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
	\end{align*}

>>>>

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all units that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

@@

		Intuitively the choice of $w = a$ is optimal (it it is the most natural with $w = 1$).
		The following is a description of the algorithm\footnote{No optimizations are described here (early stopping etc.)} :
		\begin{algorithm}
		\caption{$w$-sum of sum \label{asumsum}}
		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{Evolution of error rate for increasing number of stored messages, 2 activities per cluster, 4 clusters, 512 units per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result (for one iteration) in continuous black}
			\label{erasuresth}
		\end{figure}

@@

	The probability for all good neurons of a correct cluster (resp. of an erroneous cluster) to achieve a score equal or greater than $x$, with at least one having a score of $x$ is $P_{ac} (x) = \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = x)^k P(n_{agc} > x)^{a-k}$ (resp. $P_e(x) = \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k}$)

%	\begin{align*}
%	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
%	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
%	\end{align*}
		\begin{align*}
	&P_{retrieve} = \left [ \sum_{x = 1}^{a(c-1) + \gamma} P_{ac}(x) P(n_{bc} < x)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{x = 1}^{a(c-1) +\gamma} P_e(x) P(n_{be} < x)^{l-2a} P(n_{abe} < x)^a \right ]^{c_e} \numberthis \label{from_err_th}
	\end{align*}

	with the approximation that there is few activated units that should be kept active in an erronenous cluster.
